Verifying Demonstrations

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Breaks out formal verification to own section (fixes #38)

\subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}

@@

\begin{proof}
  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with the following:
  \begin{enumerate}
    \item guess which challenge the verifier will use and request the correct 
      response from the prover, receiving the challenge first would taint the 
      session (\cref{TaintedMF});
    \item guess the second response.
  \end{enumerate}

@@

\subsection{Formal Verification}

We wanted to formally verify the protocol security properties. To realize this, 
we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
originally the possibility to reason on time and space in its model.
However, thanks to a recent work by \textcite{TamarinDB}, all the common 
properties mentioned in the previous subsection can be equivalently 
characterized with a causality-based definition relying only on the order of 
messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
We are currently investigating the Tamarin interactive mode to validate as well the security properties.

>>>>

\subsection{\Acl*{ZK} and \acl*{PK}}\label{nbit-ZKPK}

@@

\begin{proof}
  It follows from the \ac{ZK} property (\cref{nbit-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with the following:
  \begin{enumerate}
    \item guess which challenge the verifier will use and request the correct 
      response from the prover, receiving the challenge first would taint the 
      session (\cref{TaintedMF});
    \item guess the second response.
  \end{enumerate}

@@
